### 2014-12-02 writing/F'14 paper/sick.tex
Paper TODO tweaks
One more TODO.

We also supplemented the SICK training data\footnote{We tuned the model using performance on a held out development set, but report performance here for a version of the model trained on both the training and development data and tested on the SICK test set.} with TODO examples of entailment data from the Denotation Graph project \cite{hodoshimage}, a corpus of automatically labeled (and thus noisy) entailment examples over image captions, the same genre of text from which SICK was drawn. We trained a single model on data from both sources, but used a separate set of softmax parameters for classifying into the labels from each source. We parsed the data from both sources with the Stanford PCFG Parser v. 3.3.1 \cite{klein2003accurate}. We also found that we were able to train a working model much more quickly with an additional technique: we collapse subtrees that were identical across both sentences in a pair down to a single head word. Finally, in order to improve regularization on the noisier data, we used dropout \cite{hinton2012improving} at the input to the comparison layer (10\%) and at the output from the embedding transform layer (25\%).

\begin{table}[tp]
  \centering \small
  \begin{tabular}{ l r@{ \ } r@{ \ } r@{ \ } }
    \toprule
    ~&\multicolumn{1}{c}{$\natind$ only} & \multicolumn{1}{c}{??d RNN}  & \multicolumn{1}{c}{??d RNTN}\\
    \midrule
    Test & 56.7 &	...& \textbf{75.5} \\
    Train &- &- &-  \\
    \bottomrule
  \end{tabular}
  \caption{Performance on SICK.}
  \label{sresultstable}
\end{table}

>>>>

We also supplemented the SICK training data\footnote{We tuned the model using performance on a held out development set, but report performance here for a version of the model trained on both the training and development data and tested on the SICK test set.} with \mynote{TODO} examples of entailment data from the Denotation Graph project \cite{hodoshimage}, a corpus of automatically labeled (and thus noisy) entailment examples over image captions, the same genre of text from which SICK was drawn. We trained a single model on data from both sources, but used a separate set of softmax parameters for classifying into the labels from each source. We parsed the data from both sources with the Stanford PCFG Parser v. 3.3.1 \cite{klein2003accurate}. We also found that we were able to train a working model much more quickly with an additional technique: we collapse subtrees that were identical across both sentences in a pair down to a single head word. Finally, in order to improve regularization on the noisier data, we used dropout \cite{hinton2012improving} at the input to the comparison layer (10\%) and at the output from the embedding transform layer (25\%).

\begin{table}[tp]
  \centering \small
  \begin{tabular}{ l r@{ \ } r@{ \ } r@{ \ } }
    \toprule
    ~&\multicolumn{1}{c}{$\natind$ only} & \multicolumn{1}{c}{??d RNN}  & \multicolumn{1}{c}{??d RNTN}\\
    \midrule
    Test & 56.7 &	...& \textbf{75.5} \\
    Train &- &- &-  \\
    \bottomrule
  \end{tabular}
  \caption{\mynote{Performance on SICK.}}
  \label{sresultstable}
\end{table}
